---
title: "R Notebook"
output: html_notebook
---
```{r Importing libraries}
library(dplyr)
library(tidyr)
library(zoo)
library(crqa)
library(nonlinearTseries)
library(TSA)
library(Kendall)
library(ggplot2)
set.seed(42)
``` 

```{r Load Datasets}
headers = c("Index", "LS_diff", "RS_diff")
left_df_1 <- read.csv(".\\OpenPose\\1\\left_dataframe.csv")
left_df_1 <- left_df_1[, c("X", "LS_diff", "RS_diff")]
left_df_1 <- left_df_1[-1,]

left_df_2 <- read.csv(".\\OpenPose\\2\\left_dataframe.csv")
left_df_2 <- left_df_2[, c("X", "LS_diff", "RS_diff")]
left_df_2 <- left_df_2[-1,]

left_df_3 <- read.csv(".\\OpenPose\\3\\left_dataframe.csv")
left_df_3 <- left_df_3[, c("X", "LS_diff", "RS_diff")]
left_df_3 <- left_df_3[-1,]

left_df_4 <- read.csv(".\\OpenPose\\4\\left_dataframe.csv")
left_df_4 <- left_df_4[, c("X", "LS_diff", "RS_diff")]
left_df_4 <- left_df_4[-1,]

left_df_5 <- read.csv(".\\OpenPose\\5\\left_dataframe.csv")
left_df_5 <- left_df_5[, c("X", "LS_diff", "RS_diff")]
left_df_5 <- left_df_5[-1,]

right_df_1 <- read.csv(".\\OpenPose\\1\\right_dataframe.csv")
right_df_1 <- right_df_1[, c("X", "LS_diff", "RS_diff")]
right_df_1 <- right_df_1[-1,]

right_df_2 <- read.csv(".\\OpenPose\\2\\right_dataframe.csv")
right_df_2 <- right_df_2[, c("X", "LS_diff", "RS_diff")]
right_df_2 <- right_df_2[-1,]

right_df_3 <- read.csv(".\\OpenPose\\3\\right_dataframe.csv")
right_df_3 <- right_df_3[, c("X", "LS_diff", "RS_diff")]
right_df_3 <- right_df_3[-1,]

right_df_4 <- read.csv(".\\OpenPose\\4\\right_dataframe.csv")
right_df_4 <- right_df_4[, c("X", "LS_diff", "RS_diff")]
right_df_4 <- right_df_4[-1,]

right_df_5 <- read.csv(".\\OpenPose\\5\\right_dataframe.csv")
right_df_5 <- right_df_5[, c("X", "LS_diff", "RS_diff")]
right_df_5 <- right_df_5[-1,]
```

```{r Load Sample Datasets}
headers = c("Index", "LS_diff", "RS_diff")
left_df_S1 <- read.csv(".\\OpenPose\\S1\\left_dataframe.csv")
left_df_S1 <- left_df_S1[, c("X", "LS_diff", "RS_diff")]
left_df_S1 <- left_df_S1[-1,]

left_df_S2 <- read.csv(".\\OpenPose\\S2\\left_dataframe.csv")
left_df_S2 <- left_df_S2[, c("X", "LS_diff", "RS_diff")]
left_df_S2 <- left_df_S2[-1,]

left_df_S3 <- read.csv(".\\OpenPose\\S3\\left_dataframe.csv")
left_df_S3 <- left_df_S3[, c("X", "LS_diff", "RS_diff")]
left_df_S3 <- left_df_S3[-1,]

left_df_S4 <- read.csv(".\\OpenPose\\S4\\left_dataframe.csv")
left_df_S4 <- left_df_S4[, c("X", "LS_diff", "RS_diff")]
left_df_S4 <- left_df_S4[-1,]

left_df_S5 <- read.csv(".\\OpenPose\\S5\\left_dataframe.csv")
left_df_S5 <- left_df_S5[, c("X", "LS_diff", "RS_diff")]
left_df_S5 <- left_df_S5[-1,]

left_df_S6 <- read.csv(".\\OpenPose\\S6\\left_dataframe.csv")
left_df_S6 <- left_df_S6[, c("X", "LS_diff", "RS_diff")]
left_df_S6 <- left_df_S6[-1,]

left_df_S7 <- read.csv(".\\OpenPose\\S7\\left_dataframe.csv")
left_df_S7 <- left_df_S7[, c("X", "LS_diff", "RS_diff")]
left_df_S7 <- left_df_S7[-1,]

left_df_S8 <- read.csv(".\\OpenPose\\S8\\left_dataframe.csv")
left_df_S8 <- left_df_S8[, c("X", "LS_diff", "RS_diff")]
left_df_S8 <- left_df_S8[-1,]

right_df_S1 <- read.csv(".\\OpenPose\\S1\\right_dataframe.csv")
right_df_S1 <- right_df_S1[, c("X", "LS_diff", "RS_diff")]
right_df_S1 <- right_df_S1[-1,]

right_df_S2 <- read.csv(".\\OpenPose\\S2\\right_dataframe.csv")
right_df_S2 <- right_df_S2[, c("X", "LS_diff", "RS_diff")]
right_df_S2 <- right_df_S2[-1,]

right_df_S3 <- read.csv(".\\OpenPose\\S3\\right_dataframe.csv")
right_df_S3 <- right_df_S3[, c("X", "LS_diff", "RS_diff")]
right_df_S3 <- right_df_S3[-1,]

right_df_S4 <- read.csv(".\\OpenPose\\S4\\right_dataframe.csv")
right_df_S4 <- right_df_S4[, c("X", "LS_diff", "RS_diff")]
right_df_S4 <- right_df_S4[-1,]

right_df_S5 <- read.csv(".\\OpenPose\\S5\\right_dataframe.csv")
right_df_S5 <- right_df_S5[, c("X", "LS_diff", "RS_diff")]
right_df_S5 <- right_df_S5[-1,]

right_df_S6 <- read.csv(".\\OpenPose\\S6\\right_dataframe.csv")
right_df_S6 <- right_df_S6[, c("X", "LS_diff", "RS_diff")]
right_df_S6 <- right_df_S6[-1,]

right_df_S7 <- read.csv(".\\OpenPose\\S7\\right_dataframe.csv")
right_df_S7 <- right_df_S7[, c("X", "LS_diff", "RS_diff")]
right_df_S7 <- right_df_S7[-1,]

right_df_S8 <- read.csv(".\\OpenPose\\S8\\right_dataframe.csv")
right_df_S8 <- right_df_S8[, c("X", "LS_diff", "RS_diff")]
right_df_S8 <- right_df_S8[-1,]
```
```{r Excitement Score Fragments}
left_df_1$ES <- 3 
left_df_1$ES <- 3 
left_df_2$ES <- 2 
left_df_2$ES <- 2
left_df_3$ES <- 4 
left_df_3$ES <- 4
left_df_4$ES <- 3
left_df_4$ES <- 3
left_df_5$ES <- 4
left_df_5$ES <- 4

```
```{r Excitement Score Samples}
left_df_S1$ES <- 1 
left_df_S1$ES <- 1 
left_df_S2$ES <- 2 
left_df_S2$ES <- 2
left_df_S3$ES <- 2 
left_df_S3$ES <- 2
left_df_S4$ES <- 3
left_df_S4$ES <- 3
left_df_S5$ES <- 3
left_df_S5$ES <- 3
left_df_S6$ES <- 3
left_df_S6$ES <- 3
left_df_S7$ES <- 4
left_df_S8$ES <- 4
left_df_S8$ES <- 4
left_df_S8$ES <- 4
```
```{r}
ccf_line <- function(ccf_obj)
  {
  max_acf <- max(abs(ccf_obj$acf))
  max_index <- match(max_acf, abs(ccf_obj$acf))
  return(ccf_obj$lag[max_index])
  }
```
For the shoulder adjustments, we want a time series variable that is the per person per shoulder change in y


Cross recurrence analysis
Autocorrelation Functions
```{r ACF Original}
par(mar=c(3,3,3,0))
acf1 <- ccf(left_df_1$LS_diff, left_df_1$LS_diff, lag = 64)
acf2 <- ccf(left_df_2$LS_diff, left_df_2$LS_diff, lag = 64)
acf3 <- ccf(left_df_3$LS_diff, left_df_3$LS_diff, lag = 64)
acf4 <- ccf(left_df_4$LS_diff, left_df_4$LS_diff, lag = 64)
acf5 <- ccf(left_df_5$LS_diff, left_df_5$LS_diff, lag = 64)
```
```{r ACF Samples}
par(mar=c(3,3,3,0))
acfS1 <- ccf(left_df_S1$LS_diff, left_df_S1$LS_diff, lag = 60)
acfS2 <- ccf(left_df_S2$LS_diff, left_df_S2$LS_diff, lag = 60)
acfS3 <- ccf(left_df_S3$LS_diff, left_df_S3$LS_diff, lag = 60)
acfS4 <- ccf(left_df_S4$LS_diff, left_df_S4$LS_diff, lag = 60)
acfS5 <- ccf(left_df_S5$LS_diff, left_df_S5$LS_diff, lag = 60)
acfS6 <- ccf(left_df_S6$LS_diff, left_df_S6$LS_diff, lag = 60)
acfS7 <- ccf(left_df_S7$LS_diff, left_df_S7$LS_diff, lag = 60)
acfS8 <- ccf(left_df_S8$LS_diff, left_df_S8$LS_diff, lag = 60)
```

```{r Mann Kendall Tests}
MannKendall(left_df_1$LS_diff)
MannKendall(right_df_1$LS_diff)
MannKendall(left_df_2$LS_diff)
MannKendall(right_df_2$LS_diff)
MannKendall(left_df_3$LS_diff)
MannKendall(right_df_3$LS_diff)
MannKendall(left_df_4$LS_diff)
MannKendall(right_df_4$LS_diff)
MannKendall(left_df_5$LS_diff)
MannKendall(right_df_5$LS_diff)

MannKendall(left_df_S1$LS_diff)
MannKendall(right_df_S1$LS_diff)
MannKendall(left_df_S2$LS_diff)
MannKendall(right_df_S2$LS_diff)
MannKendall(left_df_S3$LS_diff)
MannKendall(right_df_S3$LS_diff)
MannKendall(left_df_S4$LS_diff)
MannKendall(right_df_S4$LS_diff)
MannKendall(left_df_S5$LS_diff)
MannKendall(right_df_S5$LS_diff)
MannKendall(left_df_S6$LS_diff)
MannKendall(right_df_S6$LS_diff)
MannKendall(left_df_S7$LS_diff)
MannKendall(right_df_S7$LS_diff)
MannKendall(left_df_S8$LS_diff)
MannKendall(right_df_S8$LS_diff)
```
Sample 3 left and right are trending, showing
None of the random samples show trend
Trend in both 3s, 
```{r}
rows <- sample(nrow(left_df_1))
left_df_shuffle = left_df_1[rows,]
```
```{r Prewhitening}
prewhiten(left_df_1$LS_diff, left_df_1$LS_diff)
```

```{r}
par(mar=c(3,3,3,0))
ccfshuffle <- ccf(left_df_shuffle$LS_diff, left_df_shuffle$LS_diff, lag = 64)

```
```{r CCF Fragments}
par(mar=c(3,3,3,0))
ccf1 <- ccf(left_df_1$LS_diff, right_df_1$LS_diff, lag = 60, ylim = c(-0.5, 0.5))
abline(v = ccf_line(ccf1), col = "red", lty = 2)
ccf2 <- ccf(left_df_2$LS_diff, right_df_2$LS_diff, lag = 60, ylim = c(-0.5, 0.5))
abline(v = ccf_line(ccf2), col = "red", lty = 2)
ccf3 <- ccf(left_df_3$LS_diff, right_df_3$LS_diff, lag = 60, ylim = c(-0.5, 0.5))
abline(v = ccf_line(ccf3), col = "red", lty = 2)
ccf4 <- ccf(left_df_4$LS_diff, right_df_4$LS_diff, lag = 60, ylim = c(-0.5, 0.5))
abline(v = ccf_line(ccf4), col = "red", lty = 2)
ccf5 <- ccf(left_df_5$LS_diff, right_df_5$LS_diff, lag = 60, ylim = c(-0.5, 0.5))
abline(v = ccf_line(ccf5), col = "red", lty = 2)
```
```{r CCF Samples}
ccfS1<- ccf(left_df_S1$LS_diff, right_df_S1$LS_diff, lag = 60, ylim = c(-0.5, 0.5))
ccfS2<- ccf(left_df_S2$LS_diff, right_df_S2$LS_diff, lag = 60, ylim = c(-0.5, 0.5))
ccfS3<- ccf(left_df_S3$LS_diff, right_df_S3$LS_diff, lag = 60, ylim = c(-0.5, 0.5))
ccfS4<- ccf(left_df_S4$LS_diff, right_df_S4$LS_diff, lag = 60, ylim = c(-0.5, 0.5))
ccfS5<- ccf(left_df_S5$LS_diff, right_df_S5$LS_diff, lag = 60, ylim = c(-0.5, 0.5))
ccfS6<- ccf(left_df_S6$LS_diff, right_df_S6$LS_diff, lag = 60, ylim = c(-0.5, 0.5))
ccfS7<- ccf(left_df_S7$LS_diff, right_df_S7$LS_diff, lag = 60, ylim = c(-0.5, 0.5))
ccfS8<- ccf(left_df_S8$LS_diff, right_df_S8$LS_diff, lag = 60, ylim = c(-0.5, 0.5))

```
```{r Plotting master graph cross correlation}
main_df <- data.frame(ccf1$acf)
main_df$two <- data.frame(ccf2$acf)
main_df$three <- data.frame(ccf3$acf)
main_df$four <- data.frame(ccf4$acf)
main_df$five <- data.frame(ccf5$acf)
main_df$mean <- data.frame(Means=rowMeans(main_df[,-1]))
main_df$sd <- apply(main_df[ ,1:5],1,sd)

Lag = ccf1$lag

ggplot(main_df, aes(x = Lag, y = mean$Means)) +
       geom_line() +
       geom_ribbon(aes(ymin = mean$Means - sd,
                       ymax = mean$Means + sd), alpha = 0.1) + 
        xlab("Lag") + 
        ylab("Mean Correlation Coefficient")+
        theme_light()
```
```{r Plotting sample master graph cross correlation}
samplemain_df <- data.frame(ccfS1$acf)
samplemain_df$two <- data.frame(ccfS2$acf)
samplemain_df$three <- data.frame(ccfS3$acf)
samplemain_df$four <- data.frame(ccfS4$acf)
samplemain_df$five <- data.frame(ccfS5$acf)
samplemain_df$six <- data.frame(ccfS6$acf)
samplemain_df$seven <- data.frame(ccfS7$acf)
samplemain_df$eight <- data.frame(ccfS8$acf)

samplemain_df$mean <- data.frame(Means=rowMeans(samplemain_df[,-1]))
samplemain_df$sd <- apply(samplemain_df[ ,1:8],1,sd)

Lag = ccfS1$lag

ggplot(samplemain_df, aes(x = Lag, y = mean$Means)) +
       geom_line() +
       geom_ribbon(aes(ymin = mean$Means - sd,
                       ymax = mean$Means + sd), alpha = 0.1) + 
        xlab("Lag") + 
        ylab("Mean Correlation Coefficient")+
        theme_light()
```

```{r Graph per score}
Lag = ccfS1$lag
main_df1 <- data.frame(ccfS1$acf)
ggplot(main_df1, aes(x = Lag, y = ccfS1.acf)) +
       geom_line() +
        xlab("Lag") + 
        ylab("Mean Correlation Coefficient")+
        theme_light()


main_df2  <- data.frame(ccfS2$acf)
main_df2$three <- data.frame(ccfS3$acf)
main_df2$two <- data.frame(ccf2$acf)
main_df2$mean <- data.frame(Means=rowMeans(main_df2[,-1]))
main_df2$sd <- apply(main_df2[ ,1:3],1,sd)

ggplot(main_df2, aes(x = Lag, y = mean$Means)) +
       geom_line() +
       geom_ribbon(aes(ymin = mean$Means - sd,
                       ymax = mean$Means + sd), alpha = 0.1) + 
        xlab("Lag") + 
        ylab("Mean Correlation Coefficient")+
        theme_light()

main_df3  <- data.frame(ccfS4$acf)
main_df3$s5 <- data.frame(ccfS5$acf)
main_df3$one <- data.frame(ccf1$acf)
main_df3$four <- data.frame(ccf4$acf)
main_df3$mean <- data.frame(Means=rowMeans(main_df3[,-1]))
main_df3$sd <- apply(main_df3[ ,1:4],1,sd)
ggplot(main_df3, aes(x = Lag, y = mean$Means)) +
       geom_line() +
       geom_ribbon(aes(ymin = mean$Means - sd,
                       ymax = mean$Means + sd), alpha = 0.1) + 
        xlab("Lag") + 
        ylab("Mean Correlation Coefficient")+
        theme_light()

main_df4 <- data.frame(ccfS6$acf)
main_df4$s7 <- data.frame(ccfS7$acf)
main_df4$three <- data.frame(ccf3$acf)
main_df4$five <- data.frame(ccf5$acf)
main_df4$mean <- data.frame(Means=rowMeans(main_df4[,-1]))
main_df4$sd <- apply(main_df4[ ,1:4],1,sd)
ggplot(main_df4, aes(x = Lag, y = mean$Means)) +
       geom_line() +
       geom_ribbon(aes(ymin = mean$Means - sd,
                       ymax = mean$Means + sd), alpha = 0.1) + 
        xlab("Lag") + 
        ylab("Mean Correlation Coefficient")+
        theme_light()

main_df5 <- data.frame(ccfS8$acf)
ggplot(main_df1, aes(x = Lag, y = ccfS8$acf)) +
       geom_line() +
        xlab("Lag") + 
        ylab("Mean Correlation Coefficient")+
        theme_light()
```
```{r Shuffle per score}
rows <- sample(nrow(main_df2))
main_df2 <- main_df2[rows,]
ggplot(main_df2, aes(x = Lag, y = mean$Means)) +
       geom_line() +
       geom_ribbon(aes(ymin = mean$Means - sd,
                       ymax = mean$Means + sd), alpha = 0.1) + 
        xlab("Lag") + 
        ylab("Mean Correlation Coefficient")+
        theme_light()

rows <- sample(nrow(main_df3))
main_df3 <- main_df3[rows,]
ggplot(main_df3, aes(x = Lag, y = mean$Means)) +
       geom_line() +
       geom_ribbon(aes(ymin = mean$Means - sd,
                       ymax = mean$Means + sd), alpha = 0.1) + 
        xlab("Lag") + 
        ylab("Mean Correlation Coefficient")+
        theme_light()

rows <- sample(nrow(main_df4))
main_df4 <- main_df4[rows,]
ggplot(main_df4, aes(x = Lag, y = mean$Means)) +
       geom_line() +
       geom_ribbon(aes(ymin = mean$Means - sd,
                       ymax = mean$Means + sd), alpha = 0.1) + 
        xlab("Lag") + 
        ylab("Mean Correlation Coefficient")+
        theme_light()
```


Cross Recurrence Analysis
Average Mutual Information

Recurrence Plot/Diagonal Recurrence Plotk
All Mutual Average Information functions have a local minimum at 1
```{r}
mutualInformation(left_df_1$LS_diff)
mutualInformation(right_df_1$LS_diff)
```
```{r}
mutualInformation(left_df_2$LS_diff)
mutualInformation(right_df_2$LS_diff)
```
```{r}
mutualInformation(left_df_3$LS_diff)
mutualInformation(right_df_3$LS_diff)
```
```{r}
mutualInformation(left_df_4$LS_diff)
mutualInformation(right_df_4$LS_diff)
```
```{r}
mutualInformation(left_df_4$LS_diff)
mutualInformation(right_df_4$LS_diff)
```
```{r}
mutualInformation(left_df_S5$LS_diff)
mutualInformation(right_df_S5$LS_diff)
mutualInformation(left_df_S6$LS_diff)
mutualInformation(right_df_S6$LS_diff)
mutualInformation(left_df_S7$LS_diff)
mutualInformation(right_df_S7$LS_diff)
mutualInformation(left_df_S8$LS_diff)
mutualInformation(right_df_S8$LS_diff)
```

```{r}
crqa_results_1 <- crqa(ts1 = left_df_1$LS_diff, ts2 = right_df_1$LS_diff, delay = 1, embed = 2, rescale = 0, radius = 0.15, normalize = 2, mindiagline = 2, minvertline = 2, tw = 0, whiteline = FALSE, recpt = FALSE, side = "both")
RP = crqa_results_1$RP
par = list(unit = 20, labelx = "Time", labely = "Time",
cols = "dodgerblue", pcex = 0.25, pch = 0,labax = seq(0,190, 20), labay = seq(0,190,20),
las = 1)
plotRP(RP, par) 
print(crqa_results_1$RR)
print(crqa_results_1$DET)
print(crqa_results_1$L)
print(crqa_results_1$maxL)
```
```{r}
crqa_results_2 <- crqa(ts1 = left_df_2$LS_diff, ts2 = right_df_2$LS_diff, delay = 1, embed = 2, rescale = 0, radius = 0.15, normalize = 2, mindiagline = 2, minvertline = 2, tw = 0, whiteline = FALSE, recpt = FALSE, side = "both")
RP = crqa_results_2$RP
par = list(unit = 20, labelx = "Time", labely = "Time",
cols = "dodgerblue", pcex = 0.25, pch = 0,labax = seq(0,190, 20), labay = seq(0,190,20),
las = 1)
plotRP(RP, par) 
```
```{r}
crqa_results_3 <- crqa(ts1 = left_df_3$LS_diff, ts2 = right_df_3$LS_diff, delay = 1, embed = 2, rescale = 0, radius = 0.15, normalize = 2, mindiagline = 2, minvertline = 2, tw = 0, whiteline = FALSE, recpt = FALSE, side = "both")
RP = crqa_results_3$RP
par = list(unit = 5, labelx = "Time", labely = "Time",
cols = "dodgerblue", pcex = 1, pch = 0,labax = seq(0,70, 5), labay = seq(0,70,5),
las = 1)
plotRP(RP, par) 
```
```{r}
crqa_results_4 <- crqa(ts1 = left_df_4$LS_diff, ts2 = right_df_4$LS_diff, delay = 1, embed = 2, rescale = 0, radius = 0.15, normalize = 2, mindiagline = 2, minvertline = 2, tw = 0, whiteline = FALSE, recpt = FALSE, side = "both")
RP = crqa_results_4$RP
par = list(unit = 5, labelx = "Time", labely = "Time",
cols = "dodgerblue", pcex = 1, pch = 0,labax = seq(0,60, 5), labay = seq(0,60,5),
las = 1)
plotRP(RP, par) 
```
```{r}
crqa_results_5 <- crqa(ts1 = left_df_5$LS_diff, ts2 = right_df_5$LS_diff, delay = 1, embed = 2, rescale = 0, radius = 0.15, normalize = 2, mindiagline = 2, minvertline = 2, tw = 0, whiteline = FALSE, recpt = FALSE, side = "both")
RP = crqa_results_5$RP
par = list(unit = 5, labelx = "Time", labely = "Time",
cols = "dodgerblue", pcex = 1, pch = 0,labax = seq(0,60, 5), labay = seq(0,60,5),
las = 1)
plotRP(RP, par) 
```
```{r}

crqa_results_shuffle <- crqa(ts1 = left_df_1shuffle$LS_diff, ts2 = right_df_1shuffle$LS_diff, delay = 1, embed = 2, rescale = 0, radius = 1, normalize = 2, mindiagline = 2, minvertline = 2, tw = 0, whiteline = FALSE, recpt = FALSE, side = "both")
RP = crqa_results_1$RP
par = list(unit = 20, labelx = "Time", labely = "Time",
cols = "dodgerblue", pcex = 0.25, pch = 0,labax = seq(0,190, 20), labay = seq(0,190,20),
las = 1)
plotRP(RP, par) 
print(crqa_results_1$RR)
print(crqa_results_1$DET)
print(crqa_results_1$L)
print(crqa_results_1$maxL)
```
```{r}
crqa_results_S1 <- crqa(ts1 = left_df_S1$LS_diff, ts2 = right_df_S1$LS_diff, delay = 1, embed = 2, rescale = 0, radius = 0.15, normalize = 2, mindiagline = 2, minvertline = 2, tw = 0, whiteline = FALSE, recpt = FALSE, side = "both")
RP = crqa_results_S1$RP
par = list(unit = 5, labelx = "Time", labely = "Time",
cols = "dodgerblue", pcex = 1, pch = 0,labax = seq(0,60, 5), labay = seq(0,60,5),
las = 1)
plotRP(RP, par) 
```
```{r}
crqa_results_S2 <- crqa(ts1 = left_df_S2$LS_diff, ts2 = right_df_S2$LS_diff, delay = 1, embed = 2, rescale = 0, radius = 0.15, normalize = 2, mindiagline = 2, minvertline = 2, tw = 0, whiteline = FALSE, recpt = FALSE, side = "both")
RP = crqa_results_S2$RP
par = list(unit = 5, labelx = "Time", labely = "Time",
cols = "dodgerblue", pcex = 1, pch = 0,labax = seq(0,60, 5), labay = seq(0,60,5),
las = 1)
plotRP(RP, par) 
```
```{r}
crqa_results_S3 <- crqa(ts1 = left_df_S3$LS_diff, ts2 = right_df_S3$LS_diff, delay = 1, embed = 2, rescale = 0, radius = 0.15, normalize = 2, mindiagline = 2, minvertline = 2, tw = 0, whiteline = FALSE, recpt = FALSE, side = "both")
RP = crqa_results_S3$RP
par = list(unit = 5, labelx = "Time", labely = "Time",
cols = "dodgerblue", pcex = 1, pch = 0,labax = seq(0,60, 5), labay = seq(0,60,5),
las = 1)
plotRP(RP, par) 
```
```{r}
crqa_results_S4 <- crqa(ts1 = left_df_S4$LS_diff, ts2 = right_df_S4$LS_diff, delay = 1, embed = 2, rescale = 0, radius = 0.15, normalize = 2, mindiagline = 2, minvertline = 2, tw = 0, whiteline = FALSE, recpt = FALSE, side = "both")
RP = crqa_results_S4$RP
par = list(unit = 5, labelx = "Time", labely = "Time",
cols = "dodgerblue", pcex = 1, pch = 0,labax = seq(0,60, 5), labay = seq(0,60,5),
las = 1)
#plotRP(RP, par) 
```
```{r}
crqa_results_S5 <- crqa(ts1 = left_df_S5$LS_diff, ts2 = right_df_S5$LS_diff, delay = 1, embed = 2, rescale = 0, radius = 0.15, normalize = 2, mindiagline = 2, minvertline = 2, tw = 0, whiteline = FALSE, recpt = FALSE, side = "both")
RP = crqa_results_S5$RP
par = list(unit = 5, labelx = "Time", labely = "Time",
cols = "dodgerblue", pcex = 1, pch = 0,labax = seq(0,60, 5), labay = seq(0,60,5),
las = 1)
#plotRP(RP, par) 
```
```{r}
crqa_results_S6 <- crqa(ts1 = left_df_S6$LS_diff, ts2 = right_df_S6$LS_diff, delay = 1, embed = 2, rescale = 0, radius = 0.15, normalize = 2, mindiagline = 2, minvertline = 2, tw = 0, whiteline = FALSE, recpt = FALSE, side = "both")
RP = crqa_results_S6$RP
par = list(unit = 5, labelx = "Time", labely = "Time",
cols = "dodgerblue", pcex = 1, pch = 0,labax = seq(0,60, 5), labay = seq(0,60,5),
las = 1)
#plotRP(RP, par) 
```
```{r}
crqa_results_S7 <- crqa(ts1 = left_df_S7$LS_diff, ts2 = right_df_S7$LS_diff, delay = 1, embed = 2, rescale = 0, radius = 0.15, normalize = 2, mindiagline = 2, minvertline = 2, tw = 0, whiteline = FALSE, recpt = FALSE, side = "both")
RP = crqa_results_S7$RP
par = list(unit = 5, labelx = "Time", labely = "Time",
cols = "dodgerblue", pcex = 1, pch = 0,labax = seq(0,60, 5), labay = seq(0,60,5),
las = 1)
#plotRP(RP, par) 
```
```{r}
crqa_results_S8 <- crqa(ts1 = left_df_S8$LS_diff, ts2 = right_df_S8$LS_diff, delay = 1, embed = 2, rescale = 0, radius = 0.15, normalize = 2, mindiagline = 2, minvertline = 2, tw = 0, whiteline = FALSE, recpt = FALSE, side = "both")
RP = crqa_results_S8$RP
par = list(unit = 5, labelx = "Time", labely = "Time",
cols = "dodgerblue", pcex = 1, pch = 0,labax = seq(0,60, 5), labay = seq(0,60,5),
las = 1)
#plotRP(RP, par) 
```


```{r}
res = drpfromts(left_df_5$LS_diff, left_df_5$LS_diff, windowsize = 100, radius = 0.15, delay = 1, embed = 2, rescale = 0,  normalize = 2, mindiagline = 2, minvertline = 2,            tw = 0, whiteline = FALSE, recpt = FALSE,                 side = 'both', method = 'crqa', metric = 'euclidean', datatype = 'continuous')

# Save out profile for plotting
profile = res$profile

``` 
```{r}
plot(-59:59, profile, type = "l", lwd = 2, xlab = "Lag", ylab = "")
```